\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 evaluation.tex
update in the evaluation

We report our experience of applying \psharp on the three case studies discussed in this paper. We aim to answer the two following questions:

@@

For MigratingTable, the upper section of the table uses the random input generator described in Section~\ref{sec:mtable:input}.  For each bug that led to at least one test failure, we manually reviewed one of the failure traces to confirm it reflected the intended bug.  For each of the remaining bugs, we repeated the test using a test case custom written to trigger that particular bug in order to confirm that the failure to detect the bug in the original test was due to unlucky random choices of inputs and schedules and not some other problem with the experimental setup.  These results are in the lower section of the table; they can serve as additional cases in which to compare the random and PCT schedulers but do not represent a testing method one could use to find unknown bugs in software.  It may have been interesting to report results for specific test cases written before we knew the bugs as mentioned in \ref{sec:mtable:input}, but we did not do so in this study.

>>>>

We report our experience of applying \psharp on the three case studies discussed in this paper. We aim to answer the following two questions:

@@

For MigratingTable, the upper section of the table uses the random input generator described in Section~\ref{sec:mtable:input}.  For each bug that led to at least one test failure, we manually reviewed one of the failure traces to confirm it reflected the intended bug.  For each of the remaining bugs, we repeated the test using a test case custom written to trigger that particular bug in order to confirm that the failure to detect the bug in the original test was due to unlucky random choices of inputs and schedules and not some other problem with the experimental setup.  These results are in the lower section of the table; they can serve as additional cases in which to compare the random and PCT schedulers but do not represent a testing method one could use to find unknown bugs in software.  It may have been interesting to report results for specific test cases written before we knew the bugs as mentioned in \ref{sec:mtable:input}, but we did not do so in this study. \PDComment{this paragraph needs to be trimmed down probably}

One of the bugs, QueryStreamedBackUpNewStream, that we found using \psharp in MigratingTable stands out because it reflects the type of oversight that tends to occur as designs evolve. Although this bug could be potentially found with other approaches, \psharp discovered it in a matter of seconds. The developers spend about 10 minutes analyzing the trace to diagnose what was happening; granted, this was after days of experience analyzing MigratingTable traces. The developers had also added their own trace output to the \psharp test harness, since \psharp's built-in trace output is too low-level and does not include event payloads and other diagnostic data that is not passed between machines.

%We started from the failure symptom: the virtual stream returned end-of-stream when according to the reference \texttt{SpecTable}, it should have returned an additional row with key 4.  We filtered the trace for actions by the same service machine and saw that $s_O$ was closed before the virtual stream had returned the row with key 4, but $s_N$ had already advanced past key 4 before the migrator inserted the row in the new table.  At first we found this phenomenon hard to believe, but soon we were convinced it reflected a gap in our design.

%This bug, which we named QueryStreamedBackUpNewStream, is in the implementation of a streaming read from the virtual table, which should return a stream of all rows in the table sorted by key.
%The essential implementation idea is to start streams $s_O$, $s_N$ from the old and new backend tables and merge the sorted streams by keeping track of the next row in each stream and returning the row with the lesser key.  In parallel, the migrator job is concurrently copying rows from the old table to the new table; we had satisfied ourselves that this concurrency would not cause any problems.  However, then we added support to the migrator job to delete the old table when it finishes copying, which triggers the virtual stream to close $s_O$.  Suppose the virtual stream is in a state in which the next row in $s_O$ has key $k_O$ and the next row in $s_N$ has key $k_N$, where $k_O < k_N$.  Further suppose that before the next read from the virtual stream, the migrator job copies a row with key $k$ ($k_O < k < k_N$) from the old table to the new table and then deletes the old table.  Since $s_O$ has not yet returned this row when it is closed and $s_N$ has already advanced to $k_N$, the row with key $k$ will be missed by the virtual stream.  A similar problem can occur if $s_N$ does not reflect rows inserted into the new table by the migrator job after $s_N$ is started, as allowed by the \texttt{IChainTable} specification.  Restarting $s_N$ when the old table is deleted fixes both variants of the bug.

% It might be nice to include excerpts of a trace like in migration-bug3-explanation.pptx.  Unfortunately, the trace in migration-bug3-explanation.pptx doesn't match my recollection of the original diagnosis, which I want to write about truthfully (the former looks like it involves a stale streaming read, while I'm fairly sure the latter involved only the $k_O < k < k_N$ case).  If it's important, I could try to get a new trace consistent with the original diagnosis. ~ Matt

%This bug took us only about 10 minutes to diagnose from the trace; granted, this is after we had days of experience analyzing MigratingTable traces and had added our own trace output to the test harness, since \psharp's built-in trace output is too low-level and does not include event payloads and other diagnostic data that is not passed between machines.

%We started from the failure symptom: the virtual stream returned end-of-stream when according to the reference \texttt{SpecTable}, it should have returned an additional row with key 4.  We filtered the trace for actions by the same service machine and saw that $s_O$ was closed before the virtual stream had returned the row with key 4, but $s_N$ had already advanced past key 4 before the migrator inserted the row in the new table.  At first we found this phenomenon hard to believe, but soon we were convinced it reflected a gap in our design.

### 2015-09-15 paper.tex

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism in the execution, e.g., arbitrary interleavings between event handlers and unexpected node failures.
State-of-the-art testing methods commonly used in industry today ---unit, integration, and stress testing--- are unable to cover many behaviors, which results in tricky bugs being missed during testing and getting exposed in production.
In this paper, we present a new approach to testing distributed storage systems.
Our approach enables the developer to \emph{test what is being executed} and is engineered to work on production code.
It significantly improves coverage of important system behaviors and allows us to discover during testing errors that are often caught after deployment.

>>>>

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism in the execution, e.g., arbitrary interleavings between event handlers and unexpected node failures.
State-of-the-art testing methods commonly used in industry today --- unit, integration, and stress testing --- are unable to cover many behaviors, which results in tricky bugs being missed during testing and getting exposed in production.
In this paper, we present a new approach to testing distributed storage systems.
Our approach enables the developer to \emph{test what is being executed} and is engineered to work on production code.
It significantly improves coverage of important system behaviors and allows us to discover during testing errors that are often caught after deployment.
